% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[sarah-stevens]{Sarah Stevens}

\startblockquote
\useURL[url1][sarahlrstevens.info][][Webpage]\from[url1] --
\useURL[url2][mailto:sarah.lr.stevens@gmail.com][][sarah.lr.stevens@gmail.com]\from[url2]
--
\useURL[url3][https://github.com/sstevens2/CV/blob/master/sstevens_CV.pdf][][CV
weblink]\from[url3]
\stopblockquote

\thinrule

\subsection[education]{Education}

\startdescription{2012-2018 (expected)}
  {\bf PhD, Microbiology Doctoral Training Program};\crlf
  University of Wisconsin - Madison

  SciMed GRS Fellow\crlf
  MDTP Recruiting Commitee - {\bf 2014-2015}\crlf
  MDTP Steering Committee - {\bf 2015-2016}
\stopdescription

\startdescription{2007-2011}
  {\bf Bachelor of Science - Molecular and Cellular Biology};\crlf
  University of Illinois Urbana - Champaign

  {\em Minor in Informatics}\crlf
  James Scholar Honors
\stopdescription

\subsection[research-experience]{Research Experience}

{\bf University of Wisconsin - Madison,
\useURL[url4][https://mcmahonlab.wisc.edu/][][McMahon Lab]\from[url4]}

Graduate Research Assistant - {\bf 2012-Present}

Determining the forces that shape population structure and how wild
bacterial populations change through time in lakes as a model system
using reference genomes (composite genomes from metagenomes and
single-cell genomes) for uncultivated but common freshwater bacteria and
metagenomic time series from several lakes.

{\bf University of Illinois Urbana - Champaign,
\useURL[url5][https://mcb.illinois.edu/faculty/profile/metcalf/][][Metcalf
Lab]\from[url5]}

Visiting Researcher - {\bf 2011-2012}

Assembled genomes from isolates belonging to the archaeal genus
{\em Methanosarcina} and analyzed shared genomic content of members of
this genus.

{\bf University of Illinois Urbana - Champaign,
\useURL[url6][https://mcb.illinois.edu/faculty/profile/rwhitakr][][Whitaker
Lab]\from[url6]}

Undergraduate Research Assistant - {\bf 2010-2011}

Studied insertion sequences in {\em Sulfolobus} islandicus in an
independent project, cultured archaea, organized sample/culture
database, cleaned-up and prepped lab equipment.

\subsection[publications]{Publications}

Garcia, S. L.*, {\bf Stevens, S. L. R.}*, Crary, B., Martinez-Garcia,
M., Stepanauskas, R., Woyke, T., Tringe, S. G., Andersson, S.,
Bertilsson, Malmstrom, R. R., McMahon, K. D. ({\em accepted at ISME
Journal}). Contrasting patterns of genome-level diversity across
distinct co-occurring freshwater bacterial populations. *Equal
contributors

He, S., {\bf Stevens, S. L. R.}, Chan, L.-K., Bertilsson, S., Glavina
del Rio, T., Tringe, S. G., Malmstrom, R. R., McMahon, K. D. (2017).
Ecophysiology of Freshwater Verrucomicrobia Inferred from
Metagenome-Assembled Genomes. mSphere.
doi:\useURL[url7][https://doi.org/10.1128/mSphere.00277-17][][10.1128/mSphere.00277-17]\from[url7]

Bendall, M. L.*, {\bf Stevens, S. L. R.}*, Chan, L.-K., Malfatti, S.,
Schwientek, P., Tremblay, J., Schackwitz, W., Martin, J., Pati, A.,
Bushnell, B., Froula, J., Kang, D., Tringe, S. G., Bertilsson, S.,
Moran, M. A., Shade, A., Newton, R. J., McMahon, K. D., Malmstrom, R. R.
(2016). Genome-wide selective sweeps and gene-specific sweeps in natural
bacterial populations. ISMEJ.
doi:\useURL[url8][https://doi.org/10.1038/ismej.2015.241][][10.1038/ismej.2015.241]\from[url8]
{\bf featured article}

*Equal contributors

\subsection[organizations]{Organizations}

\useURL[url9][http://software-carpentry.org/][][Software
Carpentry]\from[url9] {\bf and}
\useURL[url10][http://www.datacarpentry.org/][][Data
Carpentry]\from[url10]\crlf
{\em Instructor} - {\bf 2015-Present}

\useURL[url11][https://goo.gl/Pf57mb][][Computational Biology, Ecology,
and Evolution (ComBEE)]\from[url11] group\crlf
{\em Founder/Co-Chair} - {\bf 2014-2017}\crlf
- \useURL[url12][https://goo.gl/Pf57mb][][ComBEE]\from[url12] provides
an opportunity for researchers to discuss new computational tools and
learn bioinformatics skills together.\crlf
- \useURL[url13][https://goo.gl/8fcWc3][][ComBEE Python Study
Group]\from[url13] - {\bf 2014-2017}\crlf
- \useURL[url14][https://goo.gl/xKfLHf][][ComBEE R Study
Group]\from[url14] - {\bf 2015-2017}

\useURL[url15][https://github.com/datacarpentry/genomics-hackathon][][Data
Carpentry Genomics Hack-a-thon]\from[url15]\crlf
{\em Contributor} - {\bf Mar. 23-25, 2015}

\useURL[url16][http://jgi.doe.gov/][][DOE Joint Genome
Institute]\from[url16]\crlf
{\em Intern/Affiliate} - {\bf Jan. 2015-Mar. 2015}

\subsection[teaching]{Teaching}

\useURL[url17][http://software-carpentry.org/][][Software
Carpentry]\from[url17] Workshop - University of Wisconsin - Madison\crlf
{\em Instructor} -
\useURL[url18][http://uw-madison-aci.github.io/2016-01-14-uwmadison/][][{\bf Jan.
14-15, 2016}]\from[url18],
\useURL[url19][http://uw-madison-aci.github.io/2016-06-08-uwmadison/][][{\bf Jun.
08-09, 2016}]\from[url19],
\useURL[url20][https://uw-madison-aci.github.io/2017-01-12-uwmadison/][][{\bf Jan.
12-13, 2017}]\from[url20]\crlf
{\em Helper} -
\useURL[url21][https://github.com/UW-Madison-ACI/boot-camps/blob/2015-01-13/README.md][][{\bf Jan.
13-16, 2015}]\from[url21],
\useURL[url22][https://github.com/UW-Madison-ACI/boot-camps/blob/2015-06-03/README.md][][{\bf Jun.
3-4, 2015}]\from[url22],
\useURL[url23][https://uw-madison-aci.github.io/2016-08-29-uwmadison/][][{\bf Aug.
29-30, 2016}]\from[url23],
\useURL[url24][https://uw-madison-aci.github.io/2017-06-28-uwmadison-swc/][][{\bf Jun.
28-29, 2017}]\from[url24],
\useURL[url25][https://uw-madison-aci.github.io/2017-08-30-uwmadison-swc/][][{\bf Aug.
30-31, 2017}]\from[url25]

\useURL[url26][http://www.datacarpentry.org/][][Data
Carpentry]\from[url26] Workshop - University of Wisconsin - Madison\crlf
{\em Instructor} -
\useURL[url27][https://uw-madison-aci.github.io/2017-01-10-uwmadison/][][{\bf Jan.
10-11, 2017}]\from[url27],
\useURL[url28][https://uw-madison-aci.github.io/2017-08-22-uwmadison-dc/][][{\bf Aug.
22-23, 2017}]\from[url28]\crlf
{\em Helper} -
\useURL[url29][http://uw-madison-aci.github.io/2016-01-11-uwmadison/][][{\bf Jan.
11-12, 2016}]\from[url29],
\useURL[url30][http://uw-madison-aci.github.io/2016-06-01-uwmadison/][][{\bf Jun.
01-02, 2016}]\from[url30],
\useURL[url31][https://uw-madison-aci.github.io/2017-06-19-uwmadison-dc/][][{\bf Jun.
19-20, 2017}]\from[url31]

\useURL[url32][http://software-carpentry.org/][][Software
Carpentry]\from[url32] Workshop - Federal Reserve Bank, Chicago\crlf
{\em Instructor} -
\useURL[url33][http://sarahlrstevens.info/2017-08-02-chicago-frb/][][{\bf Aug.
2-3, 2017}]\from[url33]

\useURL[url34][https://sites.google.com/a/wisc.edu/combee][][ComBEE]\from[url34]
Anvio Workshop 2017 - University of Wisconsin - Madison\crlf
{\em Instructor} -
\useURL[url35][https://public.etherpad-mozilla.org/p/2017-05-24-combee-anvio][][{\bf May.
24, 2017}]\from[url35]

\useURL[url36][https://sites.google.com/a/wisc.edu/combee][][ComBEE]\from[url36]
Git/Github Workshop - University of Wisconsin - Madison\crlf
{\em Instructor} -
\useURL[url37][https://sstevens2.github.io/git-novice-mod/][][{\bf Mar.
2-3, 2017}]\from[url37]

\useURL[url38][http://software-carpentry.org/][][Software
Carpentry]\from[url38] Instructor Training - University of Wisconsin -
Madison\crlf
{\em Helper} -
\useURL[url39][https://uw-madison-aci.github.io/2016-10-24-ttt-uwmadison/][][{\bf Oct.
24-25, 2016}]\from[url39]

\useURL[url40][http://software-carpentry.org/][][Software
Carpentry]\from[url40] Workshop - University of Wisconsin -
Milwaukee\crlf
{\em Instructor} -
\useURL[url41][http://sstevens2.github.io/2016-04-25-UW-mke/][][{\bf Apr.
25-26, 2016}]\from[url41]

\useURL[url42][http://software-carpentry.org/][][Software
Carpentry]\from[url42] Workshop - Northwestern University\crlf
{\em Instructor} -
\useURL[url43][http://xuf12.github.io/2015-11-10-northwesternu/][][{\bf Nov.
10-11, 2015}]\from[url43]

McMahon Lab Git Workshop\crlf
{\em Instructor} -
\useURL[url44][https://github.com/McMahonLab/git_wksp/tree/2015-summer\#mcmahon-lab-git-workshop][][{\bf July
2015}]\from[url44]

Bioinformatics Basics: Microbial Ecology and Evolution - Illinois
Mathematics and Science Academy Intersession\crlf
{\em Instructor/Course Designer} - {\bf Jan. 2015}

Microbiology 304: Biology of Microorganisms Laboratory - University of
Wisconsin - Madison\crlf
{\em Teaching Assistant/Instructor} - {\bf Fall 2013}

\subsection[oral-presentations]{Oral Presentations}

{\bf Stevens, S. L. R.} Starting Your Own Study Group. Rebecca J. Holz
series in Research Data Management. October 2016. Madison, WI.
\useURL[url45][http://researchdata.wisc.edu/news/october-2016-brown-bag-sarah-stevens/][][Link
to Webpage/Slides]\from[url45]

{\bf Stevens, S. L. R.}, Bendall, M. L., Chan, L.-K., Malfatti, S.,
Schwientek, P., Tremblay, J., \ldots{} McMahon, K. D. Malmstrom, R. R.
Tracking Microbial Populations Through Time Using Single-cell Genomes
and Metagenomics. UW Center for Limnology Seminar. December 2015.
Madison, WI. \useURL[url46][https://goo.gl/0ge2LZ][][Link to
Slides]\from[url46]

{\bf Stevens, S. L. R.}, Bendall, M. L., Chan, L.-K., Malfatti, S.,
Schwientek, P., Tremblay, J., \ldots{} McMahon, K. D. Malmstrom, R. R.
Genome-wide and Gene-specific Selective Sweeps in Freshwater Bacterial
Populations Revealed Using Metagenomics. JF Crow Institute for the Study
of Evolution Seminar Series. October 2015. Madison, WI.
\useURL[url47][https://goo.gl/oSnDYG][][Link to Slides]\from[url47]

{\bf Stevens, S. L. R.}, Bendall, M. L., Chan, L.-K., Malfatti, S.,
Schwientek, P., Tremblay, J., \ldots{} McMahon, K. D. Malmstrom, R. R.
Genome-wide and Gene-specific Selective Sweeps in Freshwater Bacterial
Populations Revealed Using Metagenomics. 14 Symposium Society for
Aquatic Microbial Ecology. August 2015. Uppsala, Sweden
\useURL[url48][https://goo.gl/RcrxhJ][][Link to Slides]\from[url48]

{\bf Stevens, S. L. R.}, Bendall, M. L., Chan, L.-K., Malfatti, S.,
Schwientek, P., Tremblay, J., \ldots{} McMahon, K. D. Malmstrom, R. R.
Genome-wide Selective Sweeps in Natural Bacterial Populations Revealed
by Time-series Metagenomics. 15th International Symposium on Microbial
Ecology. August 2014. Seoul, South Korea.
\useURL[url49][https://goo.gl/6iunz0][][Link to Slides]\from[url49]

\subsection[poster-presentations]{Poster Presentations}

{\bf Stevens, S. L. R.}, Egan, R., Malmstrom, R.R., McMahon, K. D.
Comparative Genomics of Selected Bacterial Populations from Several
Freshwater Bog Lakes. 2017 Microbial Population Biology Gordon Research
Conference. July 2017. Andover, NH.
\useURL[url50][https://goo.gl/ZRSh9W][][Link to Poster]\from[url50]

{\bf Stevens, S. L. R.}, Egan, R., Malmstrom, R.R., McMahon, K. D.
Comparative Genomics of Selected Bacterial Populations from Several
Freshwater Bog Lakes. 2017 Microbial Population Biology Gordon Research
Seminar. July 2017. Andover, NH.
\useURL[url51][https://goo.gl/ZRSh9W][][Link to Poster]\from[url51]

{\bf Stevens, S. L. R.}, Garcia, S. L., \ldots{} McMahon, K. D.
Contrasting Patterns fo Genome-level Diversity across Distinct
Co-occurring Populations. 16th International Symposium on Microbial
Ecology. August 2016. Montreal, Canada.
\useURL[url52][https://goo.gl/8JGS52][][Link to Poster]\from[url52]

{\bf Stevens, S. L. R.}, Garcia, S. L., \ldots{} McMahon, K. D. Tracking
Distinct Freshwater Populations Through Time by Mapping Metagenomes to
Single-cell Genomes. DOE Joint Genome Institute User Meeting 2016.
Walnut Creek, CA. \useURL[url53][https://goo.gl/ShUQVn][][Link to
Poster]\from[url53]

{\bf Stevens, S. L. R.}, Bendall, M. L., \ldots{} McMahon, K. D.
Malmstrom, R. R. Genome-wide and Gene-specific Selective Sweeps in
Freshwater Bacterial Populations Revealed Using Metagenomics. 2015
Microbial Population Biology Gordon Research Conference. July 2015.
Andover, NH. \useURL[url54][https://goo.gl/rwaFKV][][Link to
Poster]\from[url54]

{\bf Stevens, S. L. R.}, Bendall, M. L., \ldots{} McMahon, K. D.
Malmstrom, R. R. Dynamics of Sequence-Discrete Bacterial Populations
Inferred Using Metagenomes. 15th International Symposium on Microbial
Ecology. August 2014. Seoul, South Korea.
\useURL[url55][https://goo.gl/qsYL32][][Link to Poster]\from[url55]

{\bf Stevens, S. L. R.}, Bendall, M. L., \ldots{} McMahon, K. D.
Malmstrom, R. R. Dynamics of Sequence-Discrete Bacterial Populations
Inferred Using Metagenomes. SciMed GRS Poster Session 2014. September
2014. Madison, WI.

{\bf Stevens, S. L. R.}, Bendall, M. L., \ldots{} McMahon, K. D.
Malmstrom, R. R. Dynamics of Sequence-Discrete Bacterial Populations
Inferred Using Metagenomes. DOE Joint Genome Institute User Meeting
2014. Walnut Creek, CA. \useURL[url56][https://goo.gl/1voTvB][][Link to
Poster]\from[url56]

\subsection[awards]{Awards}

UW-Madison Dept. of Bacteriology Travel Award - {\bf Spring 2017}\crlf
UW-Madison Dept. of Bacteriology Betley-Allen Fellowship -
{\bf 2016-2017}\crlf
UW-Madison Graduate School Travel Award - {\bf Fall 2015}\crlf
UW-Madison Dept. of Bacteriology Travel Award - {\bf Spring 2014}

\startblockquote
Sarah Stevens --
\useURL[url57][mailto:sarahlrstevens@gmail.com][][sarahlrstevens@gmail.com]\from[url57]
-- \useURL[url58][sarahlrstevens.info]\from[url58]
\stopblockquote

\stoptext
